Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-14 docs/google-research-awards-latam/main.tex

%% \section{Related Work}
%% \Mar{rule of thumb: explain the
%%   contribution/novelty, then results achieved, and then how it relates
%% with our proposal.}
%% \Mar{this is not clear$\rightarrow$}Yang et al. \cite{yang-2011-finding} proposed CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
%% of C programs to generate invalid entries\Fix{the goal of a
%%    fuzzer is to generate valid inputs/entries. this is strange}\MAB{the
%%   goal is to generate valid programs without undefined behavior to
%%   facilitate differential testing} and
%% find bugs in several C compilers\Fix{it is strange that you don't mention differential
%%   testing, which is central in CSmith, and the use of LLVM and GCC as
%%   oracles.}.\Mar{this is just listing fuzzers. don't do this. try to
%%   follow rule of thumb above.}Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
%% that exposes the LangFuzz to generate entries based in code fragments 
%% (language grammar, sample code, test suite) and the tool Mozilla 
%% Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
%% that implements a fuzzer based on JavaScript language to improve the 
%% testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
%% \Fix{...}

>>>>

\section{Related Work}
% Differential testing with fuzzing can improve the quality of programs
% Yang et al. \cite{yang-2011-finding}

In Patra and Pradel \cite{patra2016learning} was described a new black-box fuzzer tool 
that uses generative and probabilistic models to generate the entries. To evaluate the fuzzer,
Patra and Pradel uses JavaScript and HTML documents to improve the javascript engines
in Firefox and Chrome

Hodovan and Kiss \cite{hodovan-fuzzinator} exposes the Fuzzinator\footnote{https://github.com/renatahodovan/fuzzinator}
a random testing framework that uses distincts fuzzers to generate and ran test cases one-by-one in different
program components. Fuzzinator was evaluated on JerryScript\footnote{http://jerryscript.net} 
engine

%% \Mar{rule of thumb: explain the
%%   contribution/novelty, then results achieved, and then how it relates
%% with our proposal.}
%% \Mar{this is not clear$\rightarrow$}Yang et al. \cite{yang-2011-finding} proposed CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
%% of C programs to generate invalid entries\Fix{the goal of a
%%    fuzzer is to generate valid inputs/entries. this is strange}\MAB{the
%%   goal is to generate valid programs without undefined behavior to
%%   facilitate differential testing} and
%% find bugs in several C compilers\Fix{it is strange that you don't mention differential
%%   testing, which is central in CSmith, and the use of LLVM and GCC as
%%   oracles.}.\Mar{this is just listing fuzzers. don't do this. try to
%%   follow rule of thumb above.}Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
%% that exposes the LangFuzz to generate entries based in code fragments 
%% (language grammar, sample code, test suite) and the tool Mozilla 
%% Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
%% that implements a fuzzer based on JavaScript language to improve the 
%% testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
%% \Fix{...}
